Holomorphic field theories and higher algebra

### 2022-08-29 draft.tex

\begin{prop}[\cite{FHK}, Section 1]
\label{prop: Ad} $\;$
\begin{enumerate}
\item
The dg commutative algebra $(A_d,\dbar)$ is a model for $\RR \Gamma(\pAA^d, \sO_{\rm alg})$:
\[
A_d \simeq \RR\Gamma(\pAA^{d}, \sO^{alg}) .
\]
Similarly, $(A_d^{p,*},\dbar) \simeq \RR \Gamma(\pAA^{d}, \Omega^{p}_{\rm alg})$.
\item There is a dense map of commutative bigraded algebras
\[
\jou : A^{*,*}_d \to \Omega^{*,*}(\CC^d \setminus \{0\}),
\]
and the map intertwines with the $\dbar$ and $\partial$ differentials on both sides.
\item There is a unique $\GL_d$-equivariant residue map
\[
{\rm Res}_{z=0} : A_d^{d,d-1} \to \CC
\]
such that for any $\omega \in A^{d,d-1}_d$,
\[
{\rm Res}_{z=0} (\omega) = \oint_{S^{2d-1}} \jou(\omega)
\]
where $S^{2d-1}$ is any sphere centered at the origin in $\CC^d$. 
\item There is a representative $\omega_{BM}^{\rm alg}$ of the Bochner-Martinelli kernel such that
\[
\Res_{z=0} \left(f(z) \omega_{BM}^{alg}(z,z^*) \d z_1 \cdots \d z_d\right) = f(0)
\]
for any $f (z) \in \CC[z_1,\ldots,z_d]$. 
\end{enumerate}
\end{prop}

We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\pAA^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disc) into $\fg$,
just as $\fg[z,z^{-1}]$ provides a kind of loop algebra.

>>>>

\begin{prop}[\cite{FHK}, Section 1]
\label{prop: Ad} $\;$
\begin{enumerate}
\item
The dg commutative algebra $(A_d,\dbar)$ is a model for $\RR \Gamma(\mathring{\CC}^d, \sO_{\rm alg})$:
\[
A_d \simeq \RR\Gamma(\mathring{\CC}^{d}, \sO^{alg}) .
\]
Similarly, $(A_d^{p,*},\dbar) \simeq \RR \Gamma(\mathring{\CC}^{d}, \Omega^{p}_{\rm alg})$.
\item There is a dense map of commutative bigraded algebras
\[
\jou : A^{*,*}_d \to \Omega^{*,*}(\CC^d \setminus \{0\}),
\]
and the map intertwines with the $\dbar$ and $\partial$ differentials on both sides.
\item There is a unique $\GL_d$-equivariant residue map
\[
{\rm Res}_{z=0} : A_d^{d,d-1} \to \CC
\]
such that for any $\omega \in A^{d,d-1}_d$,
\[
{\rm Res}_{z=0} (\omega) = \oint_{S^{2d-1}} \jou(\omega)
\]
where $S^{2d-1}$ is any sphere centered at the origin in $\CC^d$. 
\item There is a representative $\omega_{BM}^{\rm alg}$ of the Bochner-Martinelli kernel such that
\[
\Res_{z=0} \left(f(z) \omega_{BM}^{alg}(z,z^*) \d z_1 \cdots \d z_d\right) = f(0)
\]
for any $f (z) \in \CC[z_1,\ldots,z_d]$. 
\end{enumerate}
\end{prop}

We can use this algebra and its nice properties to define a kind of ``sphere algebra'' $\Map(\mathring{\CC}^d,\fg)$ of algebraic maps from the punctured affine space (or the punctured formal disc) into $\fg$,
just as $\fg[z,z^{-1}]$ provides a kind of loop algebra.
